A Proof-of-Concept for Explainable Disease Diagnosis\\ Using Large Language Models and\\ Answer Set Programming

### 2025-12-30 paper/draft.tex
Update title
Signed-off-by: Evangelos Lamprou <vagos@lamprou.xyz>

\title[\sys: A PoC for Explainable Disease Diagnosis Using LLMs \& ASP]{\sys: A Proof-of-Concept for Explainable Disease Diagnosis Using Large Language Models and Answer Set Programming}

>>>>

\title[A PoC for Explainable Disease Diagnosis Using LLMs \& ASP]{A Proof-of-Concept for Explainable Disease Diagnosis\\ Using Large Language Models and\\ Answer Set Programming}
